The \project{unRAVE} catalog

### 2016-09-07 article/unrave.tex
Add Reid; updates to text, etc

% RAVE builders
\author{Joss Bland-Hawthorn, Brad K. Gibson, Arnaud Siebert, Olivier Bienayme, Julio F. Navarro, Ulisse Munari}
% Bland-Hawthorn: Sydney Institute for Astronomy, School of Physics, University of Sydney, NSW 2006, Australia.
% Gibson: E.A. Milne Centre for Astrophysics, University of Hull, Hull, HU6 7RX, United Kingdom.
% Siebert: Observatoire astronomique de Strasbourg, Universit\'e de Strasbourg, CNRS, UMR 7550, 11 rue de l?Universit\'e, F-67000 Strasbourg, France
% Bienayme: Observatoire astronomique de Strasbourg, Universit\'e de Strasbourg, CNRS, UMR 7550, 11 rue de l?Universit\'e, F-67000 Strasbourg, France
% Navarro: Senior CIfAR Fellow; Department of Physics and Astronomy, University of Victoria, Victoria, BC, Canada V8P 5C2
% Munari: INAF Astronomical Observatory of Padova, 36012 Asiago (VI), Italy

@@

The most pronounced discrepancy is seen in the main-sequence of the Pleiades.
Like \citet{Kordopatis_2013}, we find lower $\logg$ values than what the isochrone
shown predicts.  There are two potential reasons for this discrepancy.  Firstly,
we note that theoretical isochrones often struggle to match the observed
color-magnitude diagrams for some young clusters \citep[e.g., the Pleiades, see][]{Bouy_2015}.
Secondly, the lower $\logg$ values we find near the turn-off for the Pleiades could
be explained if those stars are fast rotators. As seen in Figure \ref{fig:test-set-hrd},
for stars with S/N ratios $>10$~pixel$^{-1}$ or $>25$~pixel$^{-1}$, we find many
stars to sit slightly above the turn-off point.  The \rave\ pipeline identifies
these stars to be fast rotators, consistent with the idea that they are blue
stragglers.  Nevertheless, they are slightly higher from the turnoff point, which
may indicate a tendency for fast-rotating turn-off stars to have systematically
lower $\logg$ values, by $\approx$0.2~dex.

@@

We have presented an independent re-analysis of \rave\ spectra that makes near-maximal
use of the information content for red giant branch stars, and provides a significant
improvement in stellar parameters ($\teff$, $\logg$, [Fe/H]) over previous \rave\ data
releases.  When combined with the \tgas\ sample, these results may amount to a powerful
compendium for chemo-dynamic studies of the Milky Way.  However, our analysis has caveats.
Inferences based on these results should recognize those caveats, and acknowledge that 
these results are subject to our explicit assumptions, some of which are provably
incorrect.

@@

If we only consider the results from individual models, there are a number of cautionary
remarks that stem from the construction of the training set.  The labels for red giant 
branch stars primarily come from \apogee, where previous successes with \thecannon\
have demonstrated that \apogee\ labels based on high S/N data can be of high fidelity
\citep{Ness_2015,Ness_2016,Ho_2016,Casey_2016}.
However, the lack of metal-poor stars in the \apogee/\rave\ overlap sample produced
a tapering-off in the test set --- where \emph{no} stars had reliably reported metallicities
below that of the training set --- which forced us to construct a heterogeneous training
set.  The metal-poor stars included in this sample are from high-resolution studies
\citep{Fulbright_2010,Ruchti_2011}, but it is unknown if the stellar parameters are
of high fidelity (e.g., we have limited quality metrics available), and there is no
guarantee that the stellar parameters \emph{or} abundances are on the same scale as
\apogee\ \citep[and good reasons to believe they will not be; see][]{Smiljanic_2014}.

@@

>>>>

% RAVE builders
\author{Joss Bland-Hawthorn, Brad K. Gibson, Arnaud Siebert, Olivier Bienayme, Julio F. Navarro, Ulisse Munari, Warren Reid}
% Bland-Hawthorn: Sydney Institute for Astronomy, School of Physics, University of Sydney, NSW 2006, Australia.
% Gibson: E.A. Milne Centre for Astrophysics, University of Hull, Hull, HU6 7RX, United Kingdom.
% Siebert: Observatoire astronomique de Strasbourg, Universit\'e de Strasbourg, CNRS, UMR 7550, 11 rue de l?Universit\'e, F-67000 Strasbourg, France
% Bienayme: Observatoire astronomique de Strasbourg, Universit\'e de Strasbourg, CNRS, UMR 7550, 11 rue de l?Universit\'e, F-67000 Strasbourg, France
% Navarro: Senior CIfAR Fellow; Department of Physics and Astronomy, University of Victoria, Victoria, BC, Canada V8P 5C2
% Munari: INAF Astronomical Observatory of Padova, 36012 Asiago (VI), Italy
% Reid (1/2): Department of Physics and Astronomy, Macquarie University, Sydney, NSW 2109, Australia
% Reid (1/2): Western Sydney University, Penrith South DC, NSW 1797

@@

The most pronounced discrepancy is seen in the main-sequence of the Pleiades.
Like \citet{Kordopatis_2013}, we find lower $\logg$ values than what the isochrone
shown predicts.  \stub{Hawkins: use correct isochrone from Bouy to see if this issue is resolved.}
%  Firstly,
%we note that theoretical isochrones often struggle to match the observed
%color-magnitude diagrams for some young clusters \citep[e.g., the Pleiades, see][]{Bouy_2015}.

@@

We have derived atmospheric parameters ($\teff$, $\logg$, [Fe/H]) for all \rave\ 
spectra, as well as detailed abundances for red giant branch stars, based on an
independent re-analysis of \rave\ spectra.  Our catalog provides an excellent
complement to the current \rave\ data release \citep{Kunder_2016}.  
When combined with the \tgas\ sample, these results may amount to a powerful
compendium for chemo-dynamic studies of the Milky Way.  However, our analysis has caveats.
Inferences based on these results should recognize those caveats, and acknowledge that 
these results are subject to our explicit assumptions, some of which are provably
incorrect.

@@

If we only consider the results from individual models, there are a number of cautionary
remarks that stem from the construction of the training set.  The labels for red giant 
branch stars primarily come from \apogee, where previous successes with \thecannon\
have demonstrated that \apogee\ labels based on high S/N data can be of high fidelity
\citep{Ness_2015,Ness_2016,Ho_2016,Casey_2016b}.
However, the lack of metal-poor stars in the \apogee/\rave\ overlap sample produced
a tapering-off in the test set --- where \emph{no} stars had reliably reported metallicities
below that of the training set --- which forced us to construct a heterogeneous training
set.  The metal-poor stars included in this sample are from high-resolution studies
\citep{Fulbright_2010,Ruchti_2011}, but it is unknown if the stellar parameters are
of high fidelity (e.g., we have limited quality metrics available), and there is no
guarantee that the stellar parameters \emph{or} abundances are on the same scale as
\apogee\ \citep[and good reasons to believe they will not be; see][]{Smiljanic_2014}.

@@

\stub{Hot stars!}
